Figures

### 2019-05-23 figures/01_county_extent.Rmd
supress messages for clean pngs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
# setwd("figures")
source("../scripts/99_utils.R")
```

@@

```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3}
# counties that overlap hi ag iws with ep data
# setwd("_episodes_rmd")

@@

```{r tptn_maps, echo=FALSE, fig.width=7}
ep         <- readRDS("../data/ep.rds")

@@

```{r }
# residual autocorrelation range
pnt <- LAGOSNE::coordinatize(ep[1,])

>>>>

```{r setup, include=FALSE, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
# setwd("figures")
source("../scripts/99_utils.R")
```

@@

```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3, message=FALSE, warning=FALSE}
# counties that overlap hi ag iws with ep data
# setwd("_episodes_rmd")

@@

\pagebreak

```{r tptn_maps, echo=FALSE, fig.width=7, message=FALSE, eval=TRUE, warning=FALSE}
ep         <- readRDS("../data/ep.rds")

@@

\pagebreak
```{r autocor_range, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
# residual autocorrelation range
pnt <- LAGOSNE::coordinatize(ep[1,])

### 2019-05-23 figures/06_lulc_buffer_demo.Rmd
supress messages for clean pngs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE}
# setwd("figures")

@@

```{r cdl_viewport, fig.height=5}
# pull cdl lulc
cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
r  <- raster::raster("../data/cdl/2745.tif")

@@

```{r cdl_vs_nlcd}
# mask nlcd lulc

@@

```{r raster_resolution}
library(nadp)

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE, message=FALSE}
# setwd("figures")

@@

```{r cdl_viewport, fig.height=5, echo=FALSE, message=FALSE}
# pull cdl lulc
cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
r  <- raster::raster("../data/cdl/2745.tif")

@@

```{r cdl_vs_nlcd, echo=FALSE, message=FALSE}
# mask nlcd lulc

@@

```{r raster_resolution, echo=FALSE, message=FALSE}
library(nadp)

### 2019-05-23 figures/08_exploratory_dotplot.Rmd
supress messages for clean pngs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)

@@

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)

# ---- dotplot ----

@@

# ---- densityplots ----
library(ggforce)

>>>>

```{r setup, include=FALSE, message=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE}
pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)

@@

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
```

```{r dotplot, message=FALSE, echo=FALSE, warning=FALSE}
# ---- dotplot ----

@@

```{r densityplots, message=FALSE, echo=FALSE, warning=FALSE}
# ---- densityplots ----
library(ggforce)

### 2019-05-23 figures/09_stream_buffer.Rmd
reverse panel order
supress messages for clean pngs

```{r satellite, echo=FALSE}
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

@@

cowplot::plot_grid(gg_low_ag, gg_hi_ag)
```

>>>>

```{r satellite, echo=FALSE, message=FALSE, warning=FALSE}
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

@@

cowplot::plot_grid(gg_hi_ag, gg_low_ag)
```
